Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-01-15 lqg-strings.tex
Just polished a bit your recent addition

Let us begin by writing down the action of a string propagating in a background geometry. The background geometry is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. $X^\mu(\sigma, \tau)$ are the space-time coordinates of a point $(\sigma, \tau)$ on the worldsheet. Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $D+1$ scalar fields living on a $1+1$ worldsheet. But these fields are not scalars. They are components of a $D+1$ dim vector because they transform as elements of $SO(D,1)$ under global Lorentz transformations acting on the ambient space-time, which we take to be flat for the time being.

The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}. If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $SO(D,1)$ just takes one point in Minkowski to another point in Minkowski. The overall geometry is invariant under SO(D,1). Now, consider the case when the background geometry is not flat. Immediately you can see that the $X$'s can no longer be treated as elements of a $SO(D,1)$ vector under \textbf{global} Lorentz transformations.

Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p(M)$ at a given point $p$ of the background manifold $M$.
When we travel along some path $\mc{C} \in M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in SO(D,1)$. This group element arises from taking the holonomy of a $\mf{so}(D,1)$ Lie algebra valued connection living on $M$, along a the path $\mc{C}$.

@@

The end result is that we now have with a gauge field $\mc{A}_a^{IJ}(\sigma, \tau)$ living on the worldsheet $\Sigma$. Here the lower index $a$ is the worldsheet index and $J$ labels generators of the Lie algebra $\mf{so}(D,1)$. Remember this is a gauge field which is now living on the worldsheet. The consequence for the string action is that in order for the action to be invariant under local gauge transformations of $\mc{A}$, we have to replace the ordinary derivatives of $X^\mu$ with the gauge covariant derivative $\partial_a X^\mu \rightarrow \mc{D}_a X^\mu$, which is defined as:

\begin{equation}
	\mc{D}_a X^I(\sigma,\tau) = \partial_a X^I + g \mc{A}_a X^I,
\end{equation}
where $\mc{A}_a$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(D,1)$. We should therefore think of the embedding fields as $(D+1)$ dimensional vectors living in the fundamental representation of $SO(D,1)$.

>>>>

Let us begin by writing down the action of a string propagating in a background geometry. The background geometry is specified not in terms of a metric, but in terms of a connection $A_\mu^{IJ}$ and vielbein fields $E_\mu^I$. Further, we will require that the bulk connection and the bulk vielbein can be pulled back onto a connection $\mc{A}_{a}^{ij}$ and a dyad $e^a_i$, respectively, living on the string worldsheet $\Sigma$. $X^\mu(\tau , \sigma)$ are the space-time coordinates of a point $(\tau , \sigma)$ on the worldsheet. Now if one takes the sigma model viewpoint then the $X$'s can be viewed as $d+1$ scalar fields living on a $1+1$ worldsheet. But these fields are not really scalars. They are components of a $d+1$ dim vector since they transform with the fundamental representation of $\mathrm{SO}(d,1)$ under global Lorentz transformations acting on the ambient space-time, which we take to be flat for the time being.

The key point here is that the Lorentz transformations acting on the $X$'s are \textbf{global}. If the background geometry is taken to be Minkowski then the $X$'s become points on this manifold and $\mathrm{SO}(d,1)$ just takes one point in Minkowski to another point in Minkowski. The overall geometry is invariant under $\mathrm{SO}(d,1)$. Now, consider the case when the background geometry is not flat. Immediately you can see that the $X$'s can no longer be treated as elements of a $\mathrm{SO}(d,1)$ vector under \textbf{global} Lorentz transformations.

Instead of viewing the $X$'s as elements of a Minkowski space, we think of them as elements of the tangent space $T_p (M)$ at a given point $p$ of the background manifold $M$.
When we travel along some path $\mc{C} \subset M$ from point $p$ to point $p'$, the local Lorentz frames at the two points are, in general, related by an element of $g(p,p') \in \mathrm{SO}(d,1)$. This group element arises from taking the holonomy of a $\mf{so}(d,1)$ Lie algebra valued connection living on $M$, along a the path $\mc{C}$.

@@

The end result is that we now have with a gauge field $\mc{A}_a^{IJ}(\tau , \sigma)$ living on the worldsheet $\Sigma$. Here the lower index $a$ is the worldsheet index and $I , J$ labels the generators of the Lie algebra $\mf{so}(d,1)$. Remember this is a gauge field which is now living on the worldsheet. The consequence for the string action is that in order for the action to be invariant under local gauge transformations of $\mc{A}$, we have to replace the ordinary derivatives of $X^\mu$ with the gauge covariant derivative $\partial_a X^\mu \rightarrow \mc{D}_a X^\mu$, which is defined as:

\begin{equation}
	\mc{D}_a X^I(\tau , \sigma) = \partial_a X^I + k \mc{A}_{a J}^{I} X^J,
\end{equation}
where $\mc{A}_a^{I J}$ is a field living on $\Sigma$ which takes values in the Lie algebra $\mf{so}(d,1)$. We should therefore think of the embedding fields as $d+1$ dimensional vectors living in the fundamental representation of $\mathrm{SO}(d,1)$.
